This is the title [Article v\versionnumber]

### 2022-10-14 manuscript/manuscript.tex
More restructuring. Add first reworks to intoduce a split into a beginners part (only biotin, how to run GIST) and an advanced part (biotin-streptavidin; pitfalls, tipps and discussion of settings)
Change SASA method. Pymol instead of gistpp

The solvent accessible surface area (SASA) represents  the voxels that are close to the protein surface and occupied by oxygen water.
It represents the surface where water can go, and potentially surfaces that a ligand atom can occupy.

The surface is generated from the oxygen density (gO.dx) file using \software{gistpp}. 
A voxel is deemed to be  part of the surface if it is occupied by water (gO > 0.3) and has at least one neighboring empty voxel (gO < 0.1).

\begin{lstlisting}[style=bash]
	gistpp -op sasa -i gO.dx -o sasa.dx
\end{lstlisting}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{streptavidin_sasa_close.png}
	\caption{SASA for streptavidin focused on the binding pocket}\label{streptavidin_sasa}
\end{figure}

@@

In this example, the region defined in the binding pocket includes all voxels that are within 3.5 A of the heavy atoms of biotin.

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{streptavidin_bp.png}
	\caption{Volume of strepatividin defined around 3.5 A of biotin. }\label{streptavidin_sasa}
\end{figure}

>>>>

The solvent accessible surface (SASA) represents the interface between regions that are occupied by the solute, and those which can be accessed by the solvent.
GIST provides a very natural way of creating a SASA using an isosurface of the oxygen density gO.
It can be visualized in PyMOL as follows:

\begin{lstlisting}[style=pymol]
load ../gist.pdb
load ../gist-gO.dx
isomesh sas, gist-gO, 0.1
\end{lstlisting}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{figures/sasa-simple.png}
	\caption{SASA for streptavidin focused on the binding pocket}\label{streptavidin_sasa}
\end{figure}

@@

In this example, the region defined in the binding pocket includes all voxels that are within \SI{3.5}{\angstrom} of the heavy atoms of biotin.

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{streptavidin_bp_close.png}
	\caption{Volume of streptavidin defined around \SI{3.5}{\angstrom} of biotin. }\label{streptavidin_volume}
\end{figure}
